Probabilistic Model of Bilateral Lymphatic Spread in Head and Neck Cancer

### 2024-03-16 manuscript.qmd
sample using new lyscripts & try quarto plots

---
title: "Probabilistic Model of Bilateral Lymphatic Spread in Head and Neck Cancer"
authors:
  - name: Roman Ludwig
    orcid: 0000-0001-9434-328X
    email: roman.ludwig@usz.ch
  - name: Yoel Perez Haas
    email: yoel.perezhaas@usz.ch
  - name: Jan Unkelbach
    orcid: 0000-0002-4275-990X
    email: jan.unkelbach@usz.ch
format:
  html:
    code-fold: true
  pdf:
    keep-tex: true
    include-in-header:
    - text: |
        \usepackage{multirow}
jupyter: python3
execute: 
  cache: true
crossref:
  fig-prefix: "figure"
  tbl-prefix: "table"
  eq-prefix: "equation"
  sec-prefix: "section"
---

@@

```{python}
from emcee import backends
from corner import corner
import matplotlib.pyplot as plt
from tueplots import figsizes, fontsizes

backend = backends.HDFBackend(
  filename="models/midline_fix.hdf5",
  read_only=True,
)
samples = backend.get_chain(thin=20)
ndim = samples.shape[-1]

plt.rcParams.update(**figsizes.icml2022_full(nrows=ndim))

fig, axes = plt.subplots(nrows=ndim, sharex=True)
for i, ax in enumerate(axes):
  ax.plot(samples[:,::10,i], color="gray", alpha=0.2)
  ax.axhline(samples[200:,:,i].mean(), color="red")
  ax.set_xlim(0., samples.shape[0])
  ax.set_ylim(0., 1.)
```

>>>>

---
title: "Probabilistic Model of Bilateral Lymphatic Spread in Head and Neck Cancer"
authors:
  - name: Roman Ludwig
    orcid: 0000-0001-9434-328X
    email: roman.ludwig@usz.ch
  - name: Yoel Perez Haas
    email: yoel.perezhaas@usz.ch
  - name: Jan Unkelbach
    orcid: 0000-0002-4275-990X
    email: jan.unkelbach@usz.ch
format:
  html:
    code-fold: true
  pdf:
    keep-tex: true
    include-in-header:
    - text: |
        \usepackage{multirow}
        \usepackage{centernot}
jupyter: python3
execute: 
  cache: true
crossref:
  fig-prefix: "figure"
  tbl-prefix: "table"
  eq-prefix: "equation"
  sec-prefix: "section"
---

@@

```{python}
#| echo: false
#| label: fig-burnin-history
#| layout-ncol: 2
#| fig-cap: Monitoring quantities during the burn-in phase of the parameter sampling.
#| fig-subcap: 
#|   - "Autocorrelation time"
#|   - "log likelihood"

import pandas as pd
import matplotlib.pyplot as plt
from tueplots import figsizes, fontsizes

plt.rcParams.update(figsizes.icml2024_half())
plt.rcParams.update(fontsizes.icml2024())

burnin_history = pd.read_csv("models/midline_history.csv").set_index("steps")

plt.plot(
  burnin_history.index,
  burnin_history.acor_times,
)
plt.show()

plt.plot(
  burnin_history.index,
  burnin_history.max_log_probs,
)
plt.show()
```

@Fig-burnin-history is only a temporary placeholder for now.
